### 2013-12-17 thesis/src/chapters/chapter-7-evaluation.tex
Supply test case description with a figure and table of average deployment time for C-SAP

\section{Deployment time -- solution comparison}
\subsection{Motivation}
In this test we want to compare our solution to one of those available at the market which use \emph{OpenNebula} as an underlying tool for managing resources of a data center in terms of \textbf{deployment time}, one of the most important factors of products whose main purpose is to scale applications.
\emph{Carina} \cite{Carina} can be considered a perfect match of a solution for such a comparison and tests are ran against it.
\subsection{Description and preconditions}
\subsubsection{Service description}
The service comprises a simple java enterprise application, deployed in a master-slave configuration with one VM set as a load balancer and other nodes that serve as workers, which uses Tomcat as a web container.

TODO dodać konfigurację każdej z maszyn wirtualnych
\subsubsection{Hardware configuration}
All virtual machines were deployed on one node which had 3G RAM, AMD Athlon\texttrademark 64 X2 Dual Core Processor with each core of 2000 MHz frequency and a hard drive with a capacity of 160 GB.
\subsection{Results}

>>>>

\section{Deployment time -- solution comparison}
\subsection{Motivation}
In this test we want to compare our solution to one of those available at the market which use \emph{OpenNebula} as an underlying tool for managing resources of a data center and \emph{OpenVZ} as a hypervisor in terms of \textbf{deployment time}, one of the most important factors of products whose main purpose is to scale applications.
\emph{Carina} \cite{Carina} can be considered a perfect match of a solution for such a comparison and tests are ran against it.
\subsection{Description and preconditions}
This test involves the steps of
  \begin{inparaenum}[i)]
    \item instantiating one of the tested product, i.e. Cloud-SAP or Carina,
    \item ordering the deployment of a service whose specification is shown in listing \ref{lst:service-spec-test-deployment-time},
    \item measuring the time needed to set up the environment of the service.
  \end{inparaenum}
Before performing any tests all virtual machines present at the deployment node are removed.
\subsubsection{Service description}
The service comprises a simple java enterprise application, deployed in a master-slave configuration with one VM set as a load balancer and other nodes that serve as workers, which uses Tomcat as a web container.

TODO dodać konfigurację każdej z maszyn wirtualnych
\subsubsection{Hardware configuration}
All virtual machines were deployed on one node which had 3G RAM, AMD Athlon\texttrademark 64 X2 Dual Core Processor with each core of 2000 MHz frequency and a hard drive with a capacity of 160 GB.
\subsection{Results}
Obtained results are shown in table \ref{tbl:test-service-deployment-time} and in figure \ref{ch7:deployment-time-test}.

\begin{table}
  \centering
  \begin{tabular}{ c  c  c }
    \hline
    & \multicolumn{2}{c}{Solution} \\
    \cline{2-3}
    Instance no & Cloud-SAP & Carina \\
    \hline
    2 & 103.9s & x \\
    3 & 166.3s & x \\
    4 & 225.5s & x \\
    5 & 288.3s & x \\
    \hline
  \end{tabular}
  \caption{Average deployment time for the service with the various number of VMs used for the whole environment}
  \label{tbl:test-service-deployment-time}
\end{table}

\begin{figure}[!ht]
  \begin{center}
    \includegraphics{chapter-7/deployment-time-test}
  \end{center}
  \caption{Average deployment time for two competing products when the variable is the number of instances of VMs}
  \label{ch7:deployment-time-test}
\end{figure}
